Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-02-09 Journal1/Response (21-10-2019)/Response.tex

%\documentclass[12pt, draftclsnofoot, onecolumn,letterpaper]{IEEEtran}
\documentclass[12pt, letterpaper]{article}
%\documentclass[12pt, letterpaper]{IEEEtran}
\usepackage{ multirow }
\usepackage{longtable}
\usepackage{geometry}
\usepackage{ragged2e}
\usepackage[table]{xcolor}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{lipsum}
\usepackage{makeidx}
\usepackage{enumerate}
\usepackage{color}
\usepackage{refstyle}
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{nomencl}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{anysize}
\usepackage{float}
\usepackage{epstopdf}
\usepackage{threeparttable}
\usepackage{multicol}
\usepackage{amssymb}
\usepackage{adjustbox}
%\usepackage[none]{hyphenat}
%\usepackage{float}

%\usepackage{fixltx2e}
\usepackage{amsmath, amssymb, upgreek, amsthm}
\usepackage{graphicx}
\usepackage{tikz}
\geometry{letterpaper, left=20mm, right=20mm, top=20mm, bottom=20mm}
\usetikzlibrary{patterns} % LATEX and plain TEX when using Tik Z
\allowdisplaybreaks
\setlength{\textfloatsep}{2ex}
\usepackage{array}
\usepackage{enumitem}
\setlength{\parindent}{1 em}
\setlength{\parskip}{0.5 em}
\renewcommand{\baselinestretch}{1.25}
\def\dsd{d_\text{SD}}
\def\Rcoop{R_\text{Coop}}
\def\rhd{R_\text{HD}}
\def\rsd{R_\text{SD}}
\def\rsh{R_\text{SH}}
\def\Pcoops{\mathcal{P}^\text{Succ}_\text{Coop}}
\def\dsh{d_\text{SH}}
\def\dhd{d_\text{HD}}
\def\psibar{\overline{\mathcal{P}}^\text{Succ}_{i}}
\def\psbara{\overline{\mathcal{P}}^\text{Succ}_{1}}
\def\psbarb{\overline{\mathcal{P}}^\text{Succ}_{2}}
\def\psbarc{\overline{\mathcal{P}}^\text{Succ}_{3}}
\def\psbard{\overline{\mathcal{P}}^\text{Succ}_{4}}
\def\psbare{\overline{\mathcal{P}}^\text{Succ}_{5}}
\def\Ri{R_{i}}
\def\Ps{\mathcal{P}^\text{Succ}_\text{Direct}}
\def\frk{\mathrm{f}_{r_k}(r)}
\def\Rcoopj{R_\text{coop}^j}
\title{\bf \vspace*{-4ex} Statement of Responses to the Editor and the Reviewers of Paper-TCOM-TPS-19-0363.R1 \\[-6ex]}
\date{}

\begin{document}
%\vspace*{-10ex}
%\sloppy
\maketitle
We would like to thank the editor and reviewers for their comments on our manuscript.
We hope that the modifications that we have made to the manuscript, and the responses that we have
provided herein will alleviate the reviewers' concerns. Below, please find our detailed responses to the editor and reviewers' comments and suggestions.
\\ [-3.ex]
% % % % % % % % % % % % % % % Editor % % % % % % % % % % % % % % % % % % % %

\clearpage
\noindent
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Editor} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``In particular, in agreement with the reviewers, the paper would greatly benefit from a clearer focus with respect to the applicability of the discussed model specifically for nanomachines. What are the intended nanomachines? How will they be realized and what is their applicability within a synaptic cleft? How will they be implanted? A revised focus is suggested if sufficient clarity in these directions cannot be reached.''\\
\hline
\end{longtable}

\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the editor for his comment on our manuscript. According to the advances in nano-technology and nano-communications, different design strategies for intelligent nano-devices interfaced with the neuronal tissue were proposed in the literature. The proposed system model in this manuscript is based on one of them. We clarify more about this issue in the following. We refer to the following list of references in our explanation in this comment:

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{green!10}
[1] F. Patolsky, B. P. Timko, G. Yu, Y. Fang, A. B. Greytak, G. Zheng, and C. M. Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol. 313, no. 5790, pp. 1100-1104, 2006.

[2] N. Sakai, J. Mareda, and S. Matile, ``Ion channels and pores, made from scratch,'' Molecular BioSyst., vol. 3, pp. 658-666, 2007.

[3] P. Gorostiza and E. Isacoff, ``Optical switches and triggers for the manipulation of ion channels and pores,'' Molecular BioSyst., vol. 3, pp. 686-704, 2007.

[4] Mesiti, Fabio, and Ilangko Balasingham. ``Nanomachine-to-neuron communication interfaces for neuronal stimulation at nanoscale.'', IEEE Journal on Selected Areas in Communications, vol. 31, no. 12, pp. 695-704, 2013.

[5] N. Rouach, E. Avignone, W. Même, A. Koulakoff, L. Venance, F. Blomstrand, and C. Giaume, ``Gap junctions and connexin expression in the normal and pathological central nervous system,'' Biology Cell, vol. 94, no. 7-8, pp. 457-475, 2002.

[6] J. Hjorth, K. T. Blackwell, and J. Hellgren Kotaleski, ``Gap junctions between striatal fast-spiking interneurons regulate spiking activity and synchronization as a function of cortical activity'', J. Neuroscience, vol. 29, no. 16, pp. 5276-5286, 2009.

[7] R. D. Traub, M. A. Whittington, E. H. Buhl, F. E. N. LeBeau, A. Bibbig, S. Boyd, H. Cross, and T. Baldeweg, ``A possible role for gap junctions in generation of very fast EEG oscillations preceding the onset of, and perhaps initiating, seizures,'' Epilepsia, vol. 42, no. 2, pp. 153-170, 2001.
\\
\hline
\end{longtable}

\clearpage
In [1], the authors described the successful attempt to interface nano-wire (NW) FET transistors (SiNW-neurons) with soma, dendrites and axon, allowing high precision measurement and
stimulation with an array of 50 NW connections per neuron. The synthesis of ion channels and pores, assembled artificially by chemical composition were reported in [2], whereas synthetic nano-scale actuators (nano-toggles, nano-keys and nano-tweezers) to manipulate ion channels were proposed in [3].
Hence, the advances in the molecular manipulation of the matter can allow the fabrication of bio-inspired SnM interfaces.
Upon these considerations and the available nano-technology, the authors in [4] identified a set of possible SnM interface implementations. We employed one type of these interfaces in our system model according to [4] which is denoted as Gap Junction Interface.

\textbf{Gap Junction Interface [4]}:

With gap junctions, two cellular membranes in direct contact are separated by only 3 nm and for each side, clusters of \textit{connexine} (Cx36) proteins [5], combine to form a channel with diameter 1-2 nm, the \textit{connexine}, allowing bidirectional flows of ions (currents) between cells. Synthetic connexines assembled \textit{in-situ} by SnMs could allow the opening of additional ion channels on the membrane, enhancing the neuronal activity. In the following figure [4], a sample scenario with multiple SnMs attached to the target neuron is depicted. This method is motivated and supported by neuro-scientific studies [6], [7] reporting the important role of gap junctions in \textit{oscillatory behaviors} and \textit{synchronization} phenomena between neurons.

\begin{figure}[H]
\centering
\includegraphics[width=.78\textwidth,height=.3\textheight]{Gap.png}
\caption{ Diagram of a SnM based on gap junctions. The neuronal membrane is in contact with each SnM, establishing additional connexone channels which allow the flow of ions and currents [4].}
\label{new_1}
\end{figure}

% % % % % % % % % % % % % % % Reviewer 1 % % % % % % % % % % % % % % % % % % % %
\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 1} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``I thank the authors for providing a modified paper. The authors have made changes in the previous system model that struck this reviewer as the biggest limitation of the paper. The novel described solution in Figure 1 does make more sense compared to the previous one.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for careful and thorough reading of this manuscript and for the thoughtful and positive comments and constructive suggestions, which helped us to improve the quality of this manuscript. We hope that the responses provided herein can alleviate the reviewer concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 2:} ``However, the scaling problem arises now. The synaptic channel/cleft between \textbf{Tx} and \textbf{Rx} is very narrow (tens of nm). If the authors suggest nano-machines, e.g., as in the scenario shown in Figure 2 (c), both nano-machines are envisioned to co-locate in the cleft, 3 nm distant from the synaptic terminals. What is the size of nano-machines then? How realistic is that owing to the complexity of these nano-machines? Wouldn't it be much easier to consider artificial synapse instead?''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
According to the advances in nano-technology and nano-communications, different design strategies for intelligent nano-devices interfaced with the neuronal tissue were proposed in the literature. The proposed system model in this manuscript is based on one of them.
In the proposed system model, we need to consider the assumptions of real synapses since the real neurons play the role of \textbf{Tx} and \textbf{Rx} in the most of scenarios while in the artificial synapses, the assumptions are different.

About the scaling problem, the width of synaptic cleft is about tens of nm and in the worth case scenario where nano-machines are located in both terminals, 6 nm is required for SnM interfaces. Hence, there is sufficient room for nano-machines since they are much smaller than the neurons. In addition, some references in the literature discussed about the implementation of these interfaces.
We clarified about this issue in the following:

\clearpage
We refer to the following list of references in our explanation in this comment:

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{green!10}
[1] F. Patolsky, B. P. Timko, G. Yu, Y. Fang, A. B. Greytak, G. Zheng, and C. M. Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol. 313, no. 5790, pp. 1100-1104, 2006.

[2] N. Sakai, J. Mareda, and S. Matile, ``Ion channels and pores, made from scratch,'' Molecular BioSyst., vol. 3, pp. 658-666, 2007.

[3] P. Gorostiza and E. Isacoff, ``Optical switches and triggers for the manipulation of ion channels and pores,'' Molecular BioSyst., vol. 3, pp. 686-704, 2007.

[4] Mesiti, Fabio, and Ilangko Balasingham. ``Nanomachine-to-neuron communication interfaces for neuronal stimulation at nanoscale.'', IEEE Journal on Selected Areas in Communications, vol. 31, no. 12, pp. 695-704, 2013.

[5] N. Rouach, E. Avignone, W. Même, A. Koulakoff, L. Venance, F. Blomstrand, and C. Giaume, ``Gap junctions and connexin expression in the normal and pathological central nervous system,'' Biology Cell, vol. 94, no. 7-8, pp. 457-475, 2002.

[6] J. Hjorth, K. T. Blackwell, and J. Hellgren Kotaleski, ``Gap junctions between striatal fast-spiking interneurons regulate spiking activity and synchronization as a function of cortical activity'', J. Neuroscience, vol. 29, no. 16, pp. 5276-5286, 2009.

[7] R. D. Traub, M. A. Whittington, E. H. Buhl, F. E. N. LeBeau, A. Bibbig, S. Boyd, H. Cross, and T. Baldeweg, ``A possible role for gap junctions in generation of very fast EEG oscillations preceding the onset of, and perhaps initiating, seizures,'' Epilepsia, vol. 42, no. 2, pp. 153-170, 2001.
\\
\hline
\end{longtable}

\clearpage
In [1], the authors described the successful attempt to interface nano-wire (NW) FET transistors (SiNW-neurons) with soma, dendrites and axon, allowing high precision measurement and
stimulation with an array of 50 NW connections per neuron. The synthesis of ion channels and pores, assembled artificially by chemical composition were reported in [2], whereas synthetic nano-scale actuators (nano-toggles, nano-keys and nano-tweezers) to manipulate ion channels were proposed in [3].
Hence, the advances in the molecular manipulation of the matter can allow the fabrication of bio-inspired SnM interfaces.
Upon these considerations and the available nano-technology, the authors in [4] identified a set of possible SnM interface implementations. We employed one type of these interfaces in our system model according to [4] which is denoted as Gap Junction Interface.

\textbf{Gap Junction Interface [4]}:

With gap junctions, two cellular membranes in direct contact are separated by only 3 nm and for each side, clusters of \textit{connexine} (Cx36) proteins [5], combine to form a channel with diameter 1-2 nm, the \textit{connexine}, allowing bidirectional flows of ions (currents) between cells. Synthetic connexines assembled \textit{in-situ} by SnMs could allow the opening of additional ion channels on the membrane, enhancing the neuronal activity. In the following figure [4], a sample scenario with multiple SnMs attached to the target neuron is depicted. This method is motivated and supported by neuro-scientific studies [6], [7] reporting the important role of gap junctions in \textit{oscillatory behaviors} and \textit{synchronization} phenomena between neurons.

\begin{figure}[H]
\centering
\includegraphics[width=.78\textwidth,height=.3\textheight]{Gap.png}
\caption{ Diagram of a SnM based on gap junctions. The neuronal membrane is in contact with each SnM, establishing additional connexone channels which allow the flow of ions and currents [4].}
\label{new_1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\noindent
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\Centering
\cellcolor{gray!45}
\textbf{Reviewer 2} \\
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 1:} ``The paper has been improved according to the previous comments from this reviewer and only the following minor issues have remained.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for careful and thorough reading of this manuscript and
for the thoughtful comments and constructive suggestions, which help us to improve the quality of
this manuscript. We hope that the responses provided herein can alleviate the reviewer concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 2:} ``In Introduction, page 5, ``We consider a neuro-spike communication channel between two neurons located in the motor cortex region of the brain where the information is encoded by spike time intervals.''.  Please provide a reference for this sentence.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Neural coding refers to the mapping from the stimulus to the configurations of the generated
spikes by neurons. Neurons employ the spike rate coding and temporal coding to transmit information via action potentials. As we explained in the manuscript, none of the papers in the literature proposed a model for neuro-spike communication channel in the motor cortex region when temporal modulations
are employed to convey information. However, there are some papers that assumed temporal modulations in the motor cortex region. We referred to one of these papers in the new manuscript based on the reviewer comment as
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{green!10}
We consider a neuro-spike communication channel between two neurons located in the motor cortex region of the brain where the information is encoded by spike time intervals [30].
\\
\hline
\end{longtable}
The referred paper is
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{green!10}
[30] Hatsopoulos N, Geman S, Amarasingham A, Bienenstock E., ``At what time scale does the nervous system operate?'', Neurocomputing, vol. 1, no. 52, pp.25-29, 2003.
\\
\hline
\end{longtable}

\clearpage
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 3:} ``In System Model, the possibility of placing nano-machines in synapses located between motor cortex neurons must be proved. This action needs invasive surgeries, which cause further damage to the neurons.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
According to the advances in nano-technology and nano-communications, different design strategies
for intelligent nano-devices interfaced with the neuronal tissue were proposed in the literature. The
proposed system model in this manuscript is based on one of them. We clarify more about this issue in the following.
We refer to the following list of references in our explanation in this comment:

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{green!10}
[1] F. Patolsky, B. P. Timko, G. Yu, Y. Fang, A. B. Greytak, G. Zheng, and C. M. Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol. 313, no. 5790, pp. 1100-1104, 2006.

[2] N. Sakai, J. Mareda, and S. Matile, ``Ion channels and pores, made from scratch,'' Molecular BioSyst., vol. 3, pp. 658-666, 2007.

[3] P. Gorostiza and E. Isacoff, ``Optical switches and triggers for the manipulation of ion channels and pores,'' Molecular BioSyst., vol. 3, pp. 686-704, 2007.

### 2022-02-09 Journal1/paper2TNSM/pr.tex
add papers and solution

There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC). So, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice. So we have 
$\{1,2,...,S_1\}$ set of eMBB service instances, $\{1,2,...,S_2\}$ set of URLLC service instances, and
$\{1,2,...,S_3\}$ set of mMTC service instances.
Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
There are different application requests which fall into one of these service categories. Each application request requires a specific QoS. Based on the application and QoS request, UE may be admitted and allocated to the resources.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF. 
The VNFs of O-DU, O-CU-UP, and UPF are interconnected, defined as the Service Function Chain (SFC) in the O-RAN system.

Assume we have $K$ physical resource blocks (PRBs) in this system.
All $K$ PRBs can be assigned to all UEs in each service.
Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers.
In addition, there are $R$ multi-antenna O-RUs that are shared between slices. O-RU $r \in \{1,2,...,R \}$ has $J$ antennas for transmitting and receiving data. Also $\mathcal{R} = \{ r \ | \ r\in 1,2,...,R \}$ depicts the set of O-RUs. Moreover, all O-RUs have access to all PRBs.

@@

Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary variable that illustrates whether O-RU $r$ served the $i^{th}$ UE that is allocated to $s^{th}$ slice or not. 
%Here, it is assumed that each UE is served by the nearest o-RU
Also, $BN_0$ denotes the power of Gaussian additive noise.
\textcolor{Sepia}{UEs in different O-RUs can be assigned to different PRBs. As a result, a UE in O-RU $r$ using PRB $k$ may experience interference from other O-RUs in the set of $r' \in R -r$.
Network Slicing methods significantly reduce inter-service interference but do not eliminate it at all.
There are some techniques to minimize inter-slice interference. One of these techniques is to have two-time scale scheduling. The PRB scheduling to the slices is performed on the first time scale, and in the second time scale, the PRB scheduling to the UEs of slices is carried out. Since there are limited resources, inter-service interference cannot be eliminated entirely. The other method is to allocate part of the RB of eMBB services to URLLC and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}.}
We have two types of interference, the first one is between slices (inter-slice) and the second one is between UEs in each slices or services (intra-slice) that is shown in figure \ref{fig:intf}.
    \includegraphics[scale = 0.40]{Interference.png}
  \caption{Type of Interference Signal}
  \label{fig:intf}
\textcolor{teal}{ $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as follow}
%{\color{red} use paranthesis in the following equation to clear +}
\begin{subequations}\label{eqI}
&I_{r,u(s,i)}^{k} =\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
%{\color{red} $\gamma_1$ is constant used instead of variable. }
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.) 

@@

\subsubsection{PRB Scheduling}
\textcolor{Sepia}{  In this section, we study the problem of PRB scheduling to illuminate the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
We need to have an algorithm to illuminate the inter-slice interference before solving the problem \ref{problem}. Firstly, we should assign PRBs to slices, and in the second step, the assignment of PRBs of each slice to each UEs of a specific slice is performed. So, the assignment of PRB can be completed in two steps to remove inter-slice interference and isolate the slices. Firstly we assign PRBs to slices. Secondly, we allocate power of UEs, assign PRBs of slices to UEs, find the optimal number of VNFs for each slice and assign O-RU to UEs, which uses the proposed algorithm \ref{proAlg}.
Firstly, we need to find the average PRB number used by UEs in each service. Since mMTC and URLLC transmit a short packet, each UE in mMTC and URLLC requires 1 PRB. So if slice s serves mMTC or URLLC services, with $U_s$ UEs, it requires $K_s = U_s \times 1$ PRBs. For eMBB, assume the average rate of each UE in slice s serving eMBB UEs is $\bar{R}_s = Blog_2(1 + \bar{\rho_s})$, where, $\bar{\rho_s}$ is the average SNR of UEs in slice s. Also, $\mathcal{R}_{{s}}^{min}$ is the minimum data rate of each UE in slice s (eMBB slice).
So, the average number of PRB that slice s with $U_s$ UEs requires is $K_s = U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{min}}$. $K_s$ is the average number of PRBs needed for slice s, and K is the total number of PRBs in the system. Our goal is to obtain the number of PRBs assigned to each slice s ($\bar{K_s}$).

@@

\max\limits_{\boldsymbol{\bar{K_s}}} \quad &  \sum_{s=1}^{S}\delta_s \bar{\mathcal{R}}_{{s}}^{min}\log(\frac{\bar{K_s}}{K_s}) \ \\

@@

& \bar{K_s}  \leq K_s  \quad \forall s, ,\label{prb1} 

@@

@@

%\vspace*{-1em}
\section{Proposed Algorithm}\label{proAlg}
In this section, we first apply some simplifications to the system; Solving the problem \eqref{problem} is complicated since this is non-convex mixed-integer non-linear problem (MINLP) with a binary variable and an integer variable. 
We applied some simplifications and use an iterative heuristic algorithm to solve the problem.
We solve this problem in two levels, iteratively, until it converges \cite{ali2018joint}.

>>>>

There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC). So, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice. So we have 
$\{1,2,...,S_1\}$ set of eMBB service instances, $\{1,2,...,S_2\}$ set of URLLC service instances, and
$\{1,2,...,S_3\}$ set of mMTC service instances.
Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
There are different application requests which fall into one of these service categories. Each application request requires a specific QoS. Based on the application and QoS request, UE may be admitted and allocated to the resources.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF. 
The VNFs of O-DU, O-CU-UP, and UPF are interconnected, defined as the Service Function Chain (SFC) in the O-RAN system. Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers.

%All $K$ PRBs can be assigned to all UEs in each service. 
\textcolor{Sepia}{ Assume we have $K$ physical resource blocks (PRBs) in this system. Suppose each slice s consists of $\bar{K}_s$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs). Therefore, we have $\sum_s \bar{K}_s \leq K$.
}
In addition, there are $R$ multi-antenna O-RUs that are shared between slices. O-RU $r \in \{1,2,...,R \}$ has $J$ antennas for transmitting and receiving data. Also $\mathcal{R} = \{ r \ | \ r\in 1,2,...,R \}$ depicts the set of O-RUs. Moreover, all O-RUs have access to all PRBs.

@@

Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is the binary variable that illustrates whether O-RU $r$ served the $i^{th}$ UE that is allocated to $s^{th}$ slice or not. 
%Here, it is assumed that each UE is served by the nearest o-RU
Also, $BN_0$ denotes the power of Gaussian additive noise.

\textcolor{Sepia}{Interference occurs when a UE in O-RU $r$ using PRB $k$ experiences an interference signal from other O-RUs in the set of $r' \in R \not\in
 r$. UEs in each slice interfere in two ways in the technique of network slicing: the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in figure \ref{fig:intf}.
Network Slicing methods significantly reduce inter-service interference.
There are some techniques to remove inter-slice interference. One of these techniques is to have two-time scale scheduling. The PRB scheduling to the slices is performed on the first time scale, and in the second time scale, the PRB scheduling to the UEs of slices is carried out. Since there are limited resources, inter-service interference cannot be eliminated entirely. The other method is to allocate part of the RB of eMBB services to URLLC and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}.} In this paper, we assume that the PRB scheduling is performed. Also, in subsection \ref{prb}, we briefly study the PRB scheduling between slices.
\begin{figure}
  \centering 
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.40]{Interference.png}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Type of Interference Signal}
  \label{fig:intf}
\end{figure}
\textcolor{teal}{ $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as follow}
%{\color{red} use paranthesis in the following equation to clear +}
\begin{subequations}\label{eqI}
\begin{alignat}{4}
&I_{r,u(s,i)}^{k} =\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{alignat}
\end{subequations}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)
\textcolor{Sepia}{Furthermore, there is no inter-slice interference since slices are isolated and there is just intra-slice interference.}

@@

\subsubsection{PRB Scheduling}\label{prb}
\textcolor{Sepia}{ In this section, we have a brief study on the problem of PRB scheduling to eliminate  the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
We need to have an algorithm to remove the inter-slice interference before solving the problem \ref{problem}. Firstly, we should assign PRBs to slices, and in the second step, the assignment of PRBs of each slice to each UEs of a specific slice is performed. So, the assignment of PRB can be completed in two steps to remove inter-slice interference and isolate the slices. Firstly we assign PRBs to slices. Secondly, we allocate power of UEs, assign PRBs of slices to UEs, find the optimal number of VNFs for each slice and assign O-RU to UEs, which uses the proposed algorithm \ref{proAlg}.
Suppose, $\mathcal{R}_{{s}}^{min}$, and $\mathcal{R}_{{s}}^{max}$ are the minimum data rate and maximum data rate of each UE in slice s, respectively.
Firstly, we need to find the average PRB number used by UEs in each service. Since mMTC and URLLC transmit a short packet, each UE in mMTC and URLLC requires 1 PRB. So if slice s serves mMTC or URLLC services, with $U_s$ UEs, it requires $K_s = U_s \times 1$ PRBs. For eMBB, assume the average rate of each UE in slice s serving eMBB UEs is $\bar{R}_s = Blog_2(1 + \bar{\rho_s})$, where, $\bar{\rho_s}$ is the average SNR of UEs in slice s. (eMBB slice)
So, the minimum number of PRB that slice s with $U_s$ UEs requires is $K_s^{min} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{max}}}\rceil$. $K_s^{min} $ is the minimum number of PRBs needed for slice s, and K is the total number of PRBs in the system.  
Moreover, the maximum number of PRB that slice s with $U_s$ UEs requires is $K_s^{max} = \lceil{U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{min}}}\rceil$. $K_s^{max} $ is the maximum number of PRBs needed for slice s, and K is the total number of PRBs in the system. Also, $K_s = (K_s^{min}+K_s^{max})/2$ is the average number of required PRB in slice s (eMBB slice).
Our goal is to obtain the number of PRBs assigned to each slice s ($\bar{K_s}$).

@@

\max\limits_{\boldsymbol{\bar{K_s}}} \quad &  \sum_{s=1}^{S}\delta_s K_s \ln(\bar{K_s}) \ \\

@@

& K_s^{min} \leq \bar{K_s}  \leq K_s^{max}  \quad \forall s \in S_1,\label{prb1} \\
&  \bar{K_s} \leq K_s  \quad \forall s \in S_2, S_3,\label{prb2}

@@

We used logarithms to assign PRBs to all slices to make them equally fair \cite{marabissi2019highly}.
Equation \eqref{prb0} illustrates that the sum of PRBs of slices can not exceed the maximum number of PRBs. 
Equation \eqref{prb1}, restrict the number of PRBs of eMBB slices and \eqref{prb2}, limit the number of PRBs of URLLC and mMTC slices. By relaxing $\bar{K_s}$, the objective function and constraints become convex and can be solved using the Lagrangian function.

@@

\subsection{Slice Management}
\textcolor{RedViolet}{In this subsection, we want to study the management of slices. We want to talk about the creation, management, and deletion of slices.}

%\vspace*{-1em}
\section{Proposed Algorithm}\label{proAlg}
In this section, we first apply some simplifications to the system; Solving the problem \eqref{problem} is complicated since this is non-convex mixed-integer non-linear problem (MINLP) with a binary variable and an integer variable. 
We applied some simplifications and use an iterative heuristic algorithm to solve the problem.
We solve this problem in two levels, iteratively, until it converges \cite{ali2018joint}.
